---
title: "TV Shows Final Project"
author: "Samatha Bae, Isabella Fangary, Annika Hettmann, and Garrett Vetter"
subtitle: MGSC 310 Final Project
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}

# Please leave this code chunk as is. It makes some slight formatting changes to alter the output to be more aesthetically pleasing. 

library(knitr)

# Change the number in set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)


# this sets text outputted in code chunks to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = FALSE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               # change fig.width and fig.height to change the code height and width by default
               fig.width = 5.5,  
               fig.height = 4.5,
               fig.align='center')


```

```{r setup-2}

# Always print this out before your assignment
sessionInfo()
getwd()

```


```{r setup-3}

# all libraries 
library('tidyverse')
library('factoextra')
library('cluster')
library('rsample')
library('glmnet')
library('glmnetUtils')
library('forcats')
library('dplyr') 
library('knitr')
library(PerformanceAnalytics)
library(rpart)       
library(rpart.plot)  
library('randomForest')

```





# Model One: Word Sentiments
## Determine optimal number of clusters 
## Model One: Word Sentiments
# Wordcloud on Description
```{r}

Streaming_split <- initial_split(streaming_df, prop=0.75)
Streaming_train <- training(Streaming_split)
Streaming_test <- testing(Streaming_split)
filter(Streaming_test, Seasons_binary == 1)
text <- Streaming_test$Description
docs <- Corpus(VectorSource(text))
docs <- docs %>% tm_map(removeNumbers) %>% tm_map(removePunctuation) %>% tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
dtm <- TermDocumentMatrix(docs)
matrix <- as.matrix(dtm)
words <- sort(rowSums(matrix), decreasing=TRUE)
Streaming_test <- data.frame(word = names(words), freq=words)
set.seed(1884)
Streaming_words <- wordcloud(words = Streaming_test$word, freq=Streaming_test$freq, min.freq = 1, max.words = 200, random.order = FALSE, rot.per=0.35, colors = brewer.pal(8, "Dark2"))

```

# Calculated Sentiments on Description
```{r}

Streaming_split <- initial_split(streaming_df, prop=0.75)
Streaming_train <- training(Streaming_split)
Streaming_test <- testing(Streaming_split)
filter(Streaming_test, Seasons_binary == 1)
text <- Streaming_test$Description
docs <- Corpus(VectorSource(text))
docs <- docs %>% tm_map(removeNumbers) %>% tm_map(removePunctuation) %>% tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
Streaming_words <- iconv(docs)
sentiment_description <- get_nrc_sentiment(Streaming_words)
head(sentiment_description)

```

# Wordcloud on Main Genre
```{r}

Streaming_split <- initial_split(streaming_df, prop=0.75)
Streaming_train <- training(Streaming_split)
Streaming_test <- testing(Streaming_split)
filter(Streaming_test, Seasons_binary == 1)
text <- Streaming_test$Main_Genre
docs <- Corpus(VectorSource(text))
docs <- docs %>% tm_map(removeNumbers) %>% tm_map(removePunctuation) %>% tm_map(stripWhitespace)
docs <- tm_map(docs, content_transformer(tolower))
docs <- tm_map(docs, removeWords, stopwords("english"))
dtm <- TermDocumentMatrix(docs)
matrix <- as.matrix(dtm)
words <- sort(rowSums(matrix), decreasing=TRUE)
Streaming_test <- data.frame(word = names(words), freq=words)
set.seed(1884)
Streaming_genres <- wordcloud(words = Streaming_test$word, freq=Streaming_test$freq, min.freq = 1, max.words = 200, random.order = FALSE, rot.per=0.35, colors = brewer.pal(8, "Dark2"))

```


## Graph: Scatterplot
```{r}

gg <- ggplot(streaming_df, aes(x =  Seasons, y = `R Rating`)) + geom_point(aes(col = Seasons_binary)) + geom_smooth(method=lm) + labs(title = "Scatterplot of Streaming Show’s Seasons vs RT Rating", x = "Seasons", y = "Rotten Tomatoes Rating")
plot(gg)

```





# Model Two: Ridge Model 
## # Estimating Ridge Model 

```{r}
library('dplyr')

Streaming_clean <- Streaming %>%
filter(`Content Rating` != "N/A", `Content Rating` != "", `IMDB Rating` != "") %>%
mutate(Main_Genre = as.factor(unlist(map(strsplit(as.character(.$Genre), "\\,"), 1))),
Content_Rating = as.numeric(unlist(map(strsplit(as.character(.$`Content Rating`),"\\+"), 1))),
IMDB_Rating = as.numeric(`IMDB Rating`),
RT_Rating = as.numeric(`R Rating`),
Seasons = unlist(map(strsplit(as.character(.$`No of Seasons`), "[S]"), 1)),
Seasons = as.numeric(Seasons),
Streaming_Platform = strsplit(as.character(.$`Streaming Platform`),","))


View(Streaming_clean)
glimpse(Streaming_clean)

streaming_df <- Streaming_clean %>% as_tibble() %>%
mutate(Seasons_binary = as.factor(ifelse(Streaming_clean$Seasons>1, 1, 0))) %>%
mutate_if(is.character, as.factor) %>%
drop_na()

set.seed(1818)
streaming_split <- initial_split(streaming_df, prop = 0.75)
streaming_train <- training(streaming_split)
streaming_test <- testing(streaming_split)

streaming_mod_train <- cv.glmnet(Seasons_binary ~ Main_Genre + Content_Rating + IMDB_Rating + RT_Rating,
                            data = streaming_train,
                            alpha = 0,
                            family = binomial)

print(streaming_mod_train$lambda.min)

print(streaming_mod_train$lambda.1se)

coef(streaming_mod_train, s = streaming_mod1$lambda.min) %>% 
  round(3)

coef(streaming_mod_train, s = streaming_mod1$lambda.1se) %>% 
  round(3)

plot(streaming_mod_train)



streaming_mod_test <- cv.glmnet(Seasons_binary ~ Main_Genre + Content_Rating + IMDB_Rating + RT_Rating,
                            data = streaming_test,
                            alpha = 0,
                            family = binomial)

print(streaming_mod_test$lambda.min)

print(streaming_mod_test$lambda.1se)

coef(streaming_mod_test, s = streaming_mod1$lambda.min) %>% 
  round(3)

coef(streaming_mod_test, s = streaming_mod1$lambda.1se) %>% 
  round(3)

plot(streaming_mod_test)


str(streaming_mod_test)

# Training
preds_train_streaming <- predict(streaming_mod_train, newdata = streaming_train, type = "response")


# Testing
preds_test_streaming <- predict(streaming_mod_test, newdata = streaming_test, type = "response")



results_train <- data.frame(
  `truth` = streaming_train %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)),
  `Class1` = preds_train_streaming,
  `type` = rep("train",length(preds_train_streaming))
) %>% rename("Class1" = 2)

results_test <- data.frame(
  `truth` = streaming_test  %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)),
  `Class1` =  preds_test_streaming,
  `type` = rep("test",length(preds_test_streaming))
) %>% rename("Class1" = 2)

results <- bind_rows(results_train,results_test)

library('plotROC')

p_train <- ggplot(results_train,
            aes(m = Class1, d= as.numeric(Seasons_binary))) +
  geom_roc(labelsize = 3.5,
           cutoffs.at =
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16)
 
p_test <- ggplot(results_test,
            aes(m = Class1, d= as.numeric(Seasons_binary))) +
  geom_roc(labelsize = 3.5,
           cutoffs.at =
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16)


plot(p_train) +
  theme_minimal(base_size = 30)
plot(p_test)+
  theme_minimal(base_size = 30)

p <- ggplot(results,
            aes(m = Class1, d= as.numeric(Seasons_binary), color = type)) +
  geom_roc(labelsize = 3.5,
           cutoffs.at =
             c(0.99,0.9,0.7,0.5,0.3,0.1,.05, 0)) +
  theme_minimal(base_size = 16)
plot(p) +
  theme_minimal(base_size = 30)
  

calc_auc(p_test)
calc_auc(p_train)
calc_auc(p)

```



# Model Three: Lasso Model 
## # Estimating Lasso Model 

```{r}



lasso_mod_train <- cv.glmnet(Seasons_binary ~ IMDB_Rating + factor(Main_Genre) + RT_Rating + Content_Rating,
                       data = streaming_train,
                       alpha = 1,
                       family = binomial)

lasso_mod_test <- cv.glmnet(Seasons_binary ~ IMDB_Rating + factor(Main_Genre) + RT_Rating + Content_Rating,
                       data = streaming_test,
                       alpha = 1,
                       family = binomial)

minlam = lasso_mod_train$lambda.min
print(minlam)

selam = lasso_mod_train$lambda.1se

print(selam)

plot(lasso_mod_train)

coef(lasso_mod_train, s = "lambda.min")


lasso_coefs <- data.frame(
  `lasso_min` = coef(lasso_mod, s = lasso_mod$lambda.min) %>% 
    round(3) %>% as.matrix() %>% as.data.frame(),
  `lasso_1se` = coef(lasso_mod, s = lasso_mod$lambda.1se) %>% 
    round(3) %>% as.matrix() %>% as.data.frame()
) %>% rename(`lasso_min` = 1, `lasso_1se` = 2)
print(lasso_coefs)

coefpath(lasso_mod)



# Training
preds_train <- predict(lasso_mod_train, newdata = streaming_train, s = "lambda.min", type = "response")


# Testing
preds_test <- predict(lasso_mod_test, newdata = streaming_test, s = "lambda.min", type = "response")

results_train <- data.frame(
  `truth` = streaming_train %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)),
  `Class1` =  preds_train,
  `type` = rep("train",length(preds_train))
  ) %>% 
  rename("Class1" = 2)


results_test <- data.frame(
  `truth` = streaming_test  %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)),
  `Class1` =  preds_test,
  `type` = rep("test",length(preds_test))
  ) %>% 
  rename("Class1" = 2)


results <- bind_rows(results_train,results_test)

lassogg <- ggplot(results, 
            aes(m = Class1, d = as.numeric(Seasons_binary), color = type)) + 
            geom_roc(labelsize = 3.5, 
                     cutoffs.at = 
                       c(0.99, 0.9, 0.7, 0.5, 0.3, 0.1, 0)) +
            theme_minimal(base_size = 16)
            
print(lassogg)

calc_auc(lassogg)







```




# Model Four: Random Forests
## # Estimating Random Forest

```{r}



library("tidyverse")


Streaming <- 
  read_csv(here::here("datasets",
                      "All_Streaming_Shows.csv"))


Streaming_clean <- Streaming %>% 
  filter(`Content Rating` != "N/A", `Content Rating` != "", `IMDB Rating` != "") %>% 
  mutate(Main_Genre = as.factor(unlist(map(strsplit(as.character(.$Genre), "\\,"), 1))),
  Content_Rating = as.numeric(unlist(map(strsplit(as.character(.$`Content Rating`),"\\+"), 1))),
  IMDB_Rating = as.numeric(`IMDB Rating`),
  RT_Rating = as.numeric(`R Rating`),
  Seasons = unlist(map(strsplit(as.character(.$`No of Seasons`), "[S]"), 1)), 
  Seasons = as.numeric(Seasons),
  Streaming_Platform = strsplit(as.character(.$`Streaming Platform`),","))


streaming_df <- Streaming_clean %>% as_tibble() %>% 
  mutate(Seasons_binary = as.factor(ifelse(Streaming_clean$Seasons>1, 1, 0))) %>% 
  mutate_if(is.character, as.factor) %>% 
  drop_na()

set.seed(1818)
streaming_split <- initial_split(streaming_df, prop = 0.75)
streaming_train <- training(streaming_split)
streaming_test <- testing(streaming_split)


# making the radom forest model 
rf_fit_streaming <- randomForest(Seasons_binary ~ 
                         Main_Genre + Content_Rating + IMDB_Rating + 
                         RT_Rating, 
                       data = streaming_df,
                       type = classification,
                       mtry = 2,
                       na.action = na.roughfix,
                       ntree = 100, #number of models it is going to fit
                       importance = TRUE)

print(rf_fit_streaming)

# This will tells us the best number of decision trees we need 
plot(rf_fit_streaming)


# to ensure the we have the right mtry we run this code to see what the graph says is the best mtry 
rf_mods <- list()
oob_err <- NULL
test_err <- NULL
for(mtry in 1:5){
  rf_fit_streaming <- randomForest(Seasons_binary ~ 
                         Main_Genre + Content_Rating + IMDB_Rating + 
                         RT_Rating, 
                       data = streaming_df,
                       type = classification,
                       mtry = mtry,
                       na.action = na.roughfix,
                       ntree = 100, #number of models it is going to fit
                       importance = TRUE)

  oob_err[mtry] <- rf_fit_streaming$err.rate[200]
  
  cat(mtry," ")
}

results_DF <- data.frame(mtry = 1:5, oob_err)
ggplot(results_DF, aes(x = mtry, y = oob_err)) + geom_point() + theme_minimal(base_size = 16)

# partial dependence plots only changing genre
library('pdp')
pdp::partial(rf_fit_streaming, 
             pred.var = "RT_Rating", 
             plot = TRUE,
             rug = TRUE,
             plot.engine = "ggplot2",
             smooth = TRUE)

## PDP prediction interaction
library('randomForestExplainer')
plot_predict_interaction(rf_fit_streaming, 
                         streaming_df,
                         "Content_Rating",
                         "IMDB_Rating")

#to find the most important variable
importance(rf_fit_streaming, type = 1, scale = FALSE)
#to find the most important variable graphically 
varImpPlot(rf_fit_streaming, type = 1, scale = FALSE)


# min depth distribution
plot_min_depth_distribution(rf_fit_streaming)




# Training
preds_train_streaming <- predict(rf_fit_streaming, newdata = streaming_train, type = "vote") %>% 
  as_tibble() %>% select("1")

head(preds_train_streaming)


# Testing
preds_test_streaming <- predict(rf_fit_streaming, newdata = streaming_test, type = "vote") %>% 
  as_tibble() %>% select("1")

head(preds_test_streaming)



results_train <- data.frame(
  `truth` = streaming_train %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)-1),
  `Class1` = preds_train_streaming,
  `type` = rep("train",length(preds_train_streaming))
) %>% rename("Class1" = 2)

results_test <- data.frame(
  `truth` = streaming_test  %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)-1),
  `Class1` =  preds_test_streaming,
  `type` = rep("test",length(preds_test_streaming))
) %>% rename("Class1" = 2)

library('plotROC')

p_train <- ggplot(results_train, 
            aes(m = Class1, d= as.numeric(Seasons_binary))) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16)

p_test <- ggplot(results_test, 
            aes(m = Class1, d= as.numeric(Seasons_binary))) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.99,0.9,0.7,0.5,0.3,0.1,0)) +
  theme_minimal(base_size = 16)

plot(p_train)
plot(p_test)

results <- bind_rows(results_train,results_test)

p <- ggplot(results, 
            aes(m = Class1, d= as.numeric(Seasons_binary), color = type)) + 
  geom_roc(labelsize = 3.5, 
           cutoffs.at = 
             c(0.99,0.9,0.7,0.5,0.3,0.1,.05, 0)) +
  theme_minimal(base_size = 16)
print(p)

calc_auc(p_test)
calc_auc(p_train)
calc_auc(p)
```

# Model Five: Logistic Regression 
## # Estimating Logistic Regression
```{r}

logit_mod_train <- glm(Seasons_binary ~ IMDB_Rating + factor(Main_Genre) + RT_Rating + Content_Rating,
                       data = streaming_train, family = binomial)

logit_mod_test <- glm(Seasons_binary ~ IMDB_Rating + factor(Main_Genre) + RT_Rating + Content_Rating,
                       data = streaming_test, family = binomial)


summary(logit_mod_train)

exp(logit_mod_train$coefficients)


scores <- predict(logit_mod_train,
                  type = "response")

levels(streaming_train)

preds_test <- predict(logit_mod_test, newdata = streaming_test, type = "response")
preds_train <- predict(logit_mod_train, newdata = streaming_train, type = "response")

conf_mat(two_class_example, 
         truth = truth, 
         estimate = predicted)

results_train <- data.frame(
  `truth` = streaming_train %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)),
  `Class1` =  preds_train,
  `type` = rep("train",length(preds_train))
)

results_test <- data.frame(
  `truth` = streaming_test  %>% select(Seasons_binary) %>%
    mutate(Seasons_binary = as.numeric(Seasons_binary)),
  `Class1` =  preds_test,
  `type` = rep("test",length(preds_test))
)

results <- bind_rows(results_train, results_test)


logitgg <- ggplot(results, 
            aes(m = Class1, d = as.numeric(Seasons_binary), color = type)) + 
            geom_roc(labelsize = 3.5, 
                     cutoffs.at = 
                       c(0.99, 0.9, 0.7, 0.5, 0.3, 0.1, 0)) +
            theme_minimal(base_size = 16)
            
print(logitgg)

calc_auc(logitgg)
```



#Visulizations 

```{r}

library("tidyverse")


Streaming <- 
  read_csv(here::here("datasets",
                      "All_Streaming_Shows.csv"))


Streaming_clean <- Streaming %>% 
  filter(`Content Rating` != "N/A", `Content Rating` != "", `IMDB Rating` != "") %>% 
  mutate(Main_Genre = as.factor(unlist(map(strsplit(as.character(.$Genre), "\\,"), 1))),
  Content_Rating = as.numeric(unlist(map(strsplit(as.character(.$`Content Rating`),"\\+"), 1))),
  IMDB_Rating = as.numeric(`IMDB Rating`),
  RT_Rating = as.numeric(`R Rating`),
  Seasons = unlist(map(strsplit(as.character(.$`No of Seasons`), "[S]"), 1)), 
  Seasons = as.numeric(Seasons),
  Streaming_Platform = strsplit(as.character(.$`Streaming Platform`),",")) %>% 
  filter(!(Main_Genre %in% c('2020', '2019', '2018', '2017', '2016', '2015', '2014', '2013', '2012','2010','2009','2008', '2006','1997', '1981','1958', '1957','1952', '-1')))


streaming_df <- Streaming_clean %>% as_tibble() %>% 
  mutate(Seasons_binary = as.factor(ifelse(Streaming_clean$Seasons>1, 1, 0))) %>% 
  mutate_if(is.character, as.factor) %>% 
  drop_na()

set.seed(1818)
streaming_split <- initial_split(streaming_df, prop = 0.75)
streaming_train <- training(streaming_split)
streaming_test <- testing(streaming_split)

library(ggridges)
 
#1
ggplot(streaming_train, 
       aes(x = Seasons, y = Main_Genre, fill = '')) + xlim(0, 7.5) +
  geom_density_ridges()+ theme_minimal () +
  theme(legend.position = "none")+
  labs(x = 'Number of Seasons', y = 'Genre')


#2
library('ggthemes')
ggplot(streaming_train, aes(x = RT_Rating, y = Seasons)) + 
  geom_point() +
  ylim(0,20)
  theme_minimal(base_size = 16) + 
  labs(x = "Rotten Tomatoes Rating", y = 'Number of Seasons')


```
